A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-11-08 latex/main.tex
Updates from Overleaf

We then asked which single measure best explains
the number of recombination events inferred each week,
considering $n$, $H$, $n H$, $n^2$, $n^2 H$.
We included the squared number of cases each week
thinking that it might better predict co-infections.
The best single predictor of recombination events involved
the product of cases and expected heterozygosity ($n H$),
with an adjusted $R^2$ of 23.7\%.
This measure of case diversity ($n H$)
explained 49\% more of the variation in recombination events per week
than the next best predictor ($H$, adjusted $R^2$ of 15.9\%).
While consistent with the hypotheses
that recombination events occur more often when infection rates are common
and are detected more often when viral diversity is high,
we note several sources of uncertainty.
Global case numbers were under reported,
particularly during the Delta and Omicron waves~\cite{Wang2025}.
Furthermore, there may be substantial uncertainty in the timing of a recombination event,
particularly if these occur in chronically infected individuals
(as reported by \cite{Burel2022})
with substantial delays before onward cases are detected.
Finally, the filters that we applied removed all
but the most strongly supported recombination events,
although similar conclusions were obtained
when all 855 recombinants were considered (STAR Methods).

>>>>

We then asked which single measure best explains
the number of recombination events inferred each week,
considering $n$, $H$, $n H$, $n^2$, $n^2 H$.
We included the squared number of cases each week
thinking that it might better predict co-infections.
The best single predictor of recombination events involved
the product of cases and expected heterozygosity ($n H$),
with an adjusted $R^2$ of 23.7\%.
This measure of case diversity ($n H$)
explained 49\% more of the variation in recombination events per week
than the next best predictor ($H$, adjusted $R^2$ of 15.9\%).
While consistent with the hypotheses
that recombination events occur more often when infection rates are common
and are detected more often when viral diversity is high,
we note several sources of uncertainty.
Global case numbers were underreported,
particularly during the Delta and Omicron waves~\cite{Wang2025}.
Furthermore, there may be substantial uncertainty in the timing of a recombination event,
particularly if these occur in chronically infected individuals
(as reported by \cite{Burel2022})
with substantial delays before onward cases are detected.
Finally, the filters that we applied removed all
but the most strongly supported recombination events,
although similar conclusions were obtained
when all 855 recombinants detected by sc2ts were considered (STAR Methods).
